Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-15 HGmodelMANUSCRIPT/coverLETTER.tex
Update and shorten cover letter

In addition to its main message, the manuscript also provides an extensive comparison on the quality of the head group 
structures of numerous widely used lipid models in varying biologically relevant conditions. The behavior
of the lipid head group region plays a key role in multiple processes, such as partitioning of drugs or 
nanoparticles into membranes and interactions of peripheral proteins with membranes, both of which are 
currently intensively studied. Therefore the manuscript provides crucial information for a large group
of computational scientists who are struggling to select the best possible lipid model for their research.

The work has been conducted by using a novel open collaboration concept, and all the scientific contributions
are made publicly through the blog-based project web page located at \texttt{nmrlipids.blogspot.fi}. 
Thus all the scientific content related to this work (including raw data, discussions, manuscript drafts, etc.)
has been publicly available during the whole course of the project through this blog. This material and the possibility to 
discuss it on the blog page will remain available also after the publication. This approach has significantly 
increased and will further increase the scientific quality and impact of the work. In addition, we have shared 
all the simulation raw data in a format that allows easy reanalysis and therefore reuse of the data for other purposes. 
In addition to the scientic content, we believe that the success of this fresh approach in the field of chemistry 
is highly interesting to the audience of JACS.

>>>>

In addition to its main message, the manuscript also provides an extensive comparison on the structural quality 
of the numerous widely used computational lipid models. Therefore the manuscript provides crucial information 
for a large group scientists who are producing or reading the literature involving computational lipid models.

The work has been conducted by using a novel open collaboration concept, and all the scientific contributions
are made publicly through the blog-based project web page located at \texttt{nmrlipids.blogspot.fi}. 
Thus all the scientific content related to this work (including raw data, discussions, manuscript drafts, etc.)
has been publicly available during the whole course of the project through this blog. This material and the possibility to 
discuss it on the blog page will remain available also after the publication. This approach has significantly 
increased and will further increase the scientific quality and impact of the work. In addition, we have shared 
all the simulation raw data in a format that allows easy reanalysis and therefore reuse of the data for other purposes. 
In addition to the scientific content, we believe that the success of this fresh approach in the field of chemistry 
is highly interesting to the audience of JACS.
